\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{url}

% \pdfpagewidth 8.5in
% \pdfpageheight 11in

\setlength\topmargin{-0.5in}
\setlength{\textheight}{12in}

\title{Resume}
\author{York Shang-Hua, Tsai}
\date{}
\begin{document}
\section*{York Tsai (Shang-Hua, Tsai)}
\textbf{Email:} york.tw@gmail.com
\textbf{Phone:} +886 937856214

\subsection*{Experience}
\begin{itemize}
\item \textbf{VP Engineering. EZTABLE Inc. Apr 2012 - Oct 2013.}
\begin{itemize}
\item Grow the company from ten employees to over fifty employees. Lead 15+ software developers and designers while playing the software architect and dev-ops role.
\item Develop the e-voucher system, which generates 6 million USD volume of business on 2013.
\item Migrate the software stack toward Service Oriented Architecture. Design core services including: Payment, Message (GCM, APNS, email, SMS), Account, Image, Recommendation Engine and Event Tracking. Services are accessed by Thrift and RESTful protocols.
\item Bootstrap ERP, QA, Tool Chain and Data Science Team.
\end{itemize}

\item \textbf{Software Architect. EZTABLE Inc. Apr 2011 - Mar 2012.}
\begin{itemize}
\item Full-stack development with PHP, MySQL, Redis, Solr, Scribe, Resque, and Node.js.
\item Migrate servers from VPS to AWS. Utilize S3, Glacier, EC2, EBS, SES, Cloudfront, and EMR.
\item Develop front-end framework with CoffeeScript, SASS, and HAML.
\item Develop public API which is used by 3rd-party developers and business partners.
\end{itemize}

\item \textbf{Software Engineer in TCloud Computing. Trend Micro. Oct 2010 - Mar 2011.}
\begin{itemize}
\item Member of the ElasterCap project, the first PaaS in Taiwan. In charge of 1. HTTP Balancer Controller, which dynamically change the nginx reverse proxy based on status in ZooKeeper. 2. SimpleTable, a NOSQL storage based on HBase with multi-tenancy support. 3. Index \& Search based on Lucene and Solr.
\item Operate and technical support for ElasterLab, an experimental platform for ElasterCAP.
\end{itemize}

\item \textbf{Software Engineer. Taiwan Military. Oct 2009 - Aug 2010.}

\item \textbf{Software Engineer. Cazoodle Inc. Jul 2008 - Jun 2009.}
\begin{itemize}
\item Develop agent execution and data pipeline framework running on a 50 nodes cluster. Crawled data are cleaned and analyzed by entity extraction and geo-coding.
\item Develop corpus filtering system, which classifies websites based on content and link structure. The system improve its precision based on human reviewers' feedback.
\end{itemize}

\item \textbf{Software Engineer Intern. Cazoodle Inc. Oct 2006 - Jun 2008.}
\begin{itemize}
\item Develop VirtualWeb, which crawls and indexes billions of web pages. A set of APIs, including keyword search, are provided to access VirtualWeb. The system is running on a 200 nodes Hadoop cluster.
\item Implement entity search on top of VirtualWeb to find real-world entities from web pages.
\end{itemize}

\end{itemize}

\subsection*{Education}
\begin{itemize}
\item Master Degree in Computer Science and Engineering, National Chiao Tung University, Advanced Database System Lab, 2006-2008.
\item Bachelor Degree in Computer Science, National Taiwan University of Science and Technology, 2nd place, 2002-2006.
\end{itemize}

\subsection*{Publications}
\begin{itemize}
\item C.-C. Hung, W.-C. Peng, York S.-H. Tsai and W.-C. Lee, ``Exploiting Spatial and Data Correlations for Approximate Data Collection in Wireless Sensor Networks," Proceedings of the second ACM International Workshop on Knowledge Discovery from Sensor Data (In conjunction with ACM SIGKDD), Las Vegas, USA, Aug. 24. 2008.
\end{itemize}

\end{document}
